tl20-05_berghei_pir_GeneSetEnrichmentQusage

### 2021-09-14 chapter3_results_bergheiPir/Manuscript_berghei_pir_GeneSetEnrichmentQusage.Rmd
Use TPM for qusagegit push

```{r read_count_data}
berg_tpm <- read.csv('berghei_counts_newNames.csv',
                     row.names = 1)

@@

```{r generate_genesets}
pir_info <- read_xlsx('Manuscript_Frontiers_SuppInfo_berghei.xlsx',
                      sheet = 1)

pir_info <- read.table('../standard_files/Pberghei_pir_clades.txt',
                    header = TRUE)

@@

```{r lateliverstages}

@@

```{r}
livmero_livpost48.results <- lapply(
  list(pir_geneset,
       ShortLong_list,
       subfam_list), 
  function(gene_list){
    qs.results.subfam <- qusage(berg_tpm_log2plus1.mat,
                                lifeCycle_labels,
                                'Liv.Meroz-Liv.post48h',
                                gene_list,
                                n.points = 2^18)

@@

```{r}
asexRing_asexMix.results <- lapply(
  list(pir_geneset,
       subfam_list,
       ShortLong_list), 
  function(gene_list){
    qs.results.subfam <- qusage(berg_tpm_log2plus1.mat,
                                lifeCycle_labels,
                                'Asex.Ring-Asex.Mixed',
                                gene_list,
                                n.points = 2^18)

@@

Heatmap(mero_asex_malegam_stats_df_cast,
        name = 'logFoldChange',
        cluster_rows = FALSE,
        cluster_columns = FALSE,
        rect_gp = gpar(col = "white", lwd = 2),
        cell_fun = function(j, i, x, y, width, height, fill){
          fdr_val <- mero_asex_malegam_stats_df[
            mero_asex_malegam_stats_df$contrast == rownames(mero_asex_malegam_stats_df_cast[i,]),
          ]$FDR[j]
          if(fdr_val<= 0.05){
            grid.text(
              sprintf("%.3f", #One significant figure
                      fdr_val),
              x,
              y,
              gp = gpar(fontsize = 10)
            )
          }
        })

>>>>

```{r read_tpm_data}
berg_tpm <- read.csv('berghei_tpm.csv',
                     row.names = 1)

@@

```{r generate_genesets}
pir_info <- read.table('../standard_files/Pberghei_pir_clades.txt',
                    header = TRUE)

@@

lapply(maleVfemale, getElement, 'qstable')
```

```{r post48livvearlyliv}

@@

```{r livmero_livpost48}
livmero_livpost48.results <- lapply(
  list(pir_geneset,
       ShortLong_list,
       subfam_list), 
  function(gene_list){
    qs.results.subfam <- qusage(berg_tpm_log2plus1.mat,
                                lifeCycle_labels,
                                'Liv.Meroz-Liv.post48h',
                                gene_list,
                                n.points = 2^18)

@@

```{r asexRing_asexMix}
asexRing_asexMix.results <- lapply(
  list(pir_geneset,
       subfam_list,
       ShortLong_list), 
  function(gene_list){
    qs.results.subfam <- qusage(berg_tpm_log2plus1.mat,
                                lifeCycle_labels,
                                'Asex.Ring-Asex.Mixed',
                                gene_list,
                                n.points = 2^18)

@@

Heatmap(mero_asex_malegam_stats_df_cast,
        name = 'logFoldChange',
        cluster_rows = FALSE,
        cluster_columns = FALSE,
        rect_gp = gpar(col = "white", lwd = 2),
        cell_fun = function(j, i, x, y, width, height, fill){
          fdr_val <- mero_asex_malegam_stats_df[
            mero_asex_malegam_stats_df$contrast == rownames(mero_asex_malegam_stats_df_cast[i,]),
          ]$FDR[j]
          if(fdr_val<= 0.1){
            grid.text(
              sprintf("%.3f", #One significant figure
                      fdr_val),
              x,
              y,
              gp = gpar(fontsize = 10,
                        fontface = 'bold')
            )
          }
        })
